---
title: "Do Not Misstep"
author: "R. Mark Sharp"
date: "10/4/2018"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Open Ridicule By Statisticians

- Stepwise regression is important in developing prediction models only in the sense that it is important to avoid its use.

- Stepwise variable selection has done incredible damage to science.  How did we statisticians let this happen?

- A journey of a thousand hypotheses begins with a single stepwise regression

## Statistical Issues
- Yields R-squared values that are biased to be high.
- Based on methods (e.g., F tests for nested models) intended to be used to test prespecified hypotheses.
- _F_ and $\chi^2$ tests do not have the claimed distribution.
- Yields p-values that do not have the proper meaning, and the proper correction for them is a difficult problem.
- Gives biased regression coefficients that need shrinkage

## Effects
- Has severe problems in the presence of collinearity.
- Increasing the sample size does not help much.
The size of the sample was of little practical importance in determining the number of authentic variables contained in the final model.
- The number of candidate predictor variables affected the number of noise variables that gained entry to the model.
- Method yields confidence intervals for effects and predicted values that are falsely narrow

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

