---
title: "Selecting the Right Coins"
author: "R. Mark Sharp"
date: "10/5/2018"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
```

## Thought Experiment

Imagine that you have 50 pennies labeled 1 through 50 and you flip each one 10 times and write on each coin how many times it landed head side up.

```{r coin-toss-small, echo = TRUE, include = TRUE}
set.seed(123)
n_coins <- 50
tosses <- 10
p_heads <- 0.5
results <- rbinom(n_coins, tosses, p_heads)

```

I should have said, that we are looking for some lucky pennies, because I going to use the lucky pennies we find in a magic trick later. To find a lucky penny, I need to decide how many heads I need to observe to be surprised. 

I am going to cheat, because I happen to remember just enough theoretical statistics to know that when you observe a group of boolean trials, you can use the binomial distribution to calculated the probability of observing any number of one type of observation (heads) out of a known number of trials. (We are not going to show the equation, but it's a combinatorial expression with factorials so it is pretty.)

For the sake of brevity, I am going to tell you it takes a lot to surprise me.

```{r what-is-a-surprise, echo=TRUE, include = TRUE}
dbinom(7, tosses, p_heads)
dbinom(8, tosses, p_heads)
dbinom(9, tosses, p_heads)
dbinom(10, tosses, p_heads)

```
```{r set-surprises, echo=FALSE, include = TRUE}
surprise_threshhold <- 8

```

I am going to be a traditionalist here and decide I will be surprised if there are `r surprise_threshhold` or more heads out of `r tosses` tosses.

```{r find-surprises, echo=TRUE, include = TRUE}
surprise_threshhold <- 8
dbinom(surprise_threshhold, tosses, p_heads) 
picks <- seq_along(results)[results >= surprise_threshhold]
length(picks)
picks
results[results >= surprise_threshhold]

```

Let's examine what we have done and what we learned about these pennies through this experiment.

1.  I am pleased that I found so many valuable pennies out of `r n_coins`.
2.  If I want to know probability of head being tossed for each valuable coin, I just look at the count of heads and divide by the number of tosses. Fortunately, in this case I just need to move the decimal place one position to the left to get my estimate.

Now as statisticians, `r tosses` is not a big enough sample for a good estimate so let's make it bigger.

```{r lot-of-tosses}
tosses_large <- 1000
pbinom(800, tosses_large, 0.5, lower.tail = FALSE)
pbinom(550, tosses_large, 0.5, lower.tail = FALSE)
pbinom(525, tosses_large, 0.5, lower.tail = FALSE)
pbinom(526, tosses_large, 0.5, lower.tail = FALSE)

```

```{r find-surprises-more-data, echo=TRUE, include = TRUE}
surprise_threshhold_large <- 526
results_large <- rbinom(n_coins, tosses_large, p_heads)
dbinom(surprise_threshhold_large, tosses_large, p_heads) 
picks_large <- seq_along(results_large)[results_large >= surprise_threshhold_large]
length(picks_large)
picks_large
results_large[results_large >= surprise_threshhold_large]

```
